Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-05 WSSSPE3/report/wg_appendix_user_community.tex
Section 5.10 and Appendix L: small changes. DONE for today's submission deadline.

POC:
Dan Gunter\footnote{email: \href{mailto:dkgunter@lbl.gov}{dkgunter@lbl.gov}} and 
Ethan Davis\footnote{email: \href{mailto:edavis@ucar.edu}{edavis@ucar.edu}}

@@

In describing best practices, the group discussed the different modes for
starting a scientific software project: building on an existing product that
needs improving, recognizing an unsatisfied need of an existing community, or
creating a new solution to a need not yet recognized by the community. The group
also thought that the existing books on software communities would need to be
evaluated in light of differences between Science Software projects and general
OSS projects in terms of scale, science, acknowledgement and credit, and funding
models.

@@

Another next step would be increasing recognition of need for science software
projects to focus on building and supporting their user communities. Good software
engineering practices are not enough, and popular training like Software
Carpentry does not currently address this issue head on.

@@

With a small amount of seed funding, it is possible that members of this group or other parties could
spend the time necessary to devise a survey of existing projects and deploy this, probably including travel to
meetings and workshops for the various software communities.

>>>>

Point of contact:
Dan Gunter\footnote{email: \href{mailto:dkgunter@lbl.gov}{dkgunter@lbl.gov}} and 
Ethan Davis\footnote{email: \href{mailto:edavis@ucar.edu}{edavis@ucar.edu}}.

@@

In describing best practices, the group discussed the different modes for
starting a scientific software project: building on an existing product that
needs improving, recognizing an unsatisfied need of an existing community, or
creating a new solution to a need not yet recognized by the community. The group
also thought that the existing books on software communities would need to be
evaluated in light of differences between science software projects and general
open-source software (OSS) projects in terms of scale, science, acknowledgement and credit, and funding
models.

@@

Another next step would be increasing recognition of need for science software
projects to focus on building and supporting their user communities. Good software
engineering practices are not enough, and popular training like Software
Carpentry does not currently address this issue head-on.

@@

With a small amount of seed funding, it is possible that members of this group or other parties could
spend the time necessary to devise a survey of existing projects and deploy this, probably by traveling to
meetings and workshops for the various software communities.

### 2016-02-05 WSSSPE3/report/wg_main_user_community.tex
Section 5.10 and Appendix L: small changes. DONE for today's submission deadline.

Discussion revolved around a few questions: what is the benefit of having a
``community'' for software sustainability, what practices and circumstances lead
to having and maintaining a community, how can funding help or hinder this
process, and perhaps most importantly, how can best practices be described and
distilled into a document that can help new projects.

@@

The most important next steps is a ``Best Practice'' document, which would
describe what successful projects with engaged communities look like, how to
replicate this type of project, and look at end-of-life on a community project.
Another next step would be better training to increase recognition of need for science software
projects to focus on building and supporting their user communities.

@@

This group doesn't have a landing page yet. Please send requests to join and contribute to both
Dan Gunter <dkgunter@lbl.gov> and Ethan Davis <edavis@ucar.edu>.

>>>>

Discussion revolved around a few questions: what are the benefits of having a
``community'' for software sustainability; what practices and circumstances may lead
to having and maintaining a community; how can funding help or hinder this
process; and perhaps most importantly, how can best practices be described and
distilled into a document that can help new projects.

@@

The most important next steps is a ``Best Practice'' document, which would
describe what successful projects with engaged communities look like, how to
replicate this type of project, and look at the end of life of a community project.
Another next step would be better training to increase recognition of need for science software
projects to focus on building and supporting their user communities.

@@

This group does not have a landing page yet. Please send requests to join and
contribute by writing to both Dan Gunter\footnote{email:
\href{mailto:dkgunter@lbl.gov}{dkgunter@lbl.gov}} and Ethan
Davis\footnote{email: \href{mailto:edavis@ucar.edu}{edavis@ucar.edu}}.
